---
title: "p8105_hw_smm2350"
author: "Shaina Mackin"
date: 2021-09-29
output: github_document 
---

```{r tidyverse}
library(tidyverse)
```

# Problem 1

## Create data frame

The below code chunk produces a data frame comprised of:
a random sample of size 10 from a standard Normal distribution; 
a logical vector indicating whether elements of the sample are greater than 0;
a character vector of length 10; 
and a factor vector of length 10, with 3 different factor “levels”

```{r problem1_df}

problem1_df = tibble(
  norm_samp = rnorm(10, mean =1),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("Portland", "Seattle", "NYC", "LA", "Denver", "Chicago", "Boston", "Baltimore", "Atlanta", "Philadelphia"),
  vec_factor = factor(c("small", "medium", "large", "large", "medium", "medium", "small", "large", "medium", "small"))
)
 
```

## Take mean of each variable

The below code chunk attempts to take the mean of each variable in problem1_df.

```{r problem1_means}

mean_samp = mean(pull(problem1_df, norm_samp))
mean_samp = mean(pull(problem1_df, norm_samp_pos))
mean_samp = mean(pull(problem1_df, vec_char))
mean_samp = mean(pull(problem1_df, vec_factor))

```

Taking the mean of the numeric vector, norm_samp, and logical vector, norm_samp_pos, worked. Taking the mean of vec_char and vec_factor did not work because, as the warning messages indicate, neither argument is either numeric or logical. 





